Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-12-17 code/analysis.Rmd
fixed typo

p1 <- residplot(resids_exp, title = "Exponental Model")
p2 <- residplot(resids_lin, title = "Linear Model")
p3 <- varplot(resids_exp)
p4 <- varplot(resids_lin)

>>>>

p1 <- residplot(resids_exp, title = "Exponential Model")
p2 <- residplot(resids_lin, title = "Linear Model")
p3 <- varplot(resids_exp)
p4 <- varplot(resids_lin)
